Supporting Information

### 2018-04-08 SupportingInformation.Rmd
minor edit

## Abundance data for *Ceratium furca* in UK seas \label{Pns_data}
   * Plankton North sea dataset collects data at 26 locations for 22 species and for 56 years.
   * We threw out all locations that had fewer than 45 years data
   * We use species=16 [Name : "Ceratium_furca"] for Plankton_North_Sea data
   * *Ceratium furca* is a dicoflagellate commonly found in UK seas
   * note, when we edit this, we cannot call it the North Seas since data come also from other seas around the UK

@@

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for *Ceratium furca* abundance data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_pns}}
\end{center}
\end{figure}

>>>>

## Abundance data for *Ceratium furca* in UK seas \label{Pns_data}
   * Plankton North sea dataset collects data at 26 locations for 22 species and for 56 years.
   * We threw out all locations that had fewer than 45 years data
   * We use species=16 [Name : "Ceratium furca"] for Plankton_North_Sea data
   * *Ceratium furca* is a dicoflagellate commonly found in UK seas
   * note, when we edit this, we cannot call it the North Seas since data come also from other seas around the UK

@@

\begin{figure}[!h]
\textbf{ \hspace{2.6 cm} (A) \hspace{3.6 cm} (B) \hspace{3.8 cm} (C) \hspace{3.8 cm} (D)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{2.6 cm} (E) \hspace{3.6 cm} (F) \hspace{3.8 cm} (G) \hspace{3.8 cm} (H)} \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{4.8 cm} (I) \hspace{3.8 cm} (J) \hspace{4 cm} (K) } \\
\begin{center}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=1.8in]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for \textit{Ceratium furca} abundance data plotted against geographical distance $(D)$ between two sampling locations. (A) Spearman correlation vs. $D$, (B) Kendall correlation vs. $D$, (C) $\cor_l$ vs. $D$, (D) $\cor_u$ vs. $D$; (E) $\Ps_l$ vs. $D$; (F) $\Ps_u$ vs. $D$; (G) $\Dsq_u$ vs. $D$; (H) $\Dsq_l$ vs. $D$; (I) $\cor_l-\cor_u$ vs. $D$; (J) $\Ps_l-\Ps_u$ vs. $D$; (K) $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all pairs of locations. \label{fig_pns}}
\end{center}
\end{figure}
